---
title: "Mod1d_lm"
author: "runlevel0"
date: "October 25, 2015"
output: html_document
---

Before starting, there is a nice dataset here: http://www.ats.ucla.edu/stat/data/hsb2.csv

Thus: 

```{r include=FALSE}

hsb2 <- read.csv("http://www.ats.ucla.edu/stat/data/hsb2.csv")
```

### calculating slope and the linear equation in R

To find the slop (intercept) and the values of the equation I use the lm() funtction like this: 

- Given two points A= (8,10) and B=(12,16) (the way they are displayed in textbooks)

```{r}
# x <- c(A[1],B[1]) and y <- c(A[2],B[2])

x <- c(8,12)
y <- c(10,16)

lm(y ~ x)

```

The equation is $$y=2x-4$$, thus  $$y= slope*x-intercept $$

### Ploting series of coordinate pairs
*** There seems to have ben a change here as in the past it ws possible to just plot like that (not R ode as it would fail): 

     plot(list(c(1,2),c(3,5),c(4,1)))

Now this fails miserably and you need to specify the values for X and Y this way: 

```{r} 

#given the ordered pairs (1,2), (3,5) and (4,1)

x <- c(1,3,4)
y <- c(2,5,1)

plot(x,y)

```

*** For short tutorial see the SENIC howto (in html for convenience) ***

### Predicted value

The symbol for the predicted values for y is y-hat: 

$$\hat{y}=a+bx$$

being *a* (or $b_0$ for multiple regression models) the intercept (-intecept) and *b* the slope coefficient

#### Y Intercept: 

$$a=\bar{y}-b*\bar{x}$$

#### Slope Coefficient

$$b=r\left(\frac{S_y}{S_x}\right)$$

r * ratio of the SD of the Y values by the SD of the x values






