---
title: "Mod 3A Probability"
author: "Enric Martinez"
date: "5 november 2015"
output: html_document
---

## Probability (Intro)

### Resources: 

Besides the resources in eDX there is a very nice and to the point free book in cran: 

https://cran.r-project.org/web/packages/IPSUR/vignettes/IPSUR.pdf 
(or here: https://www.dropbox.com/s/aitc45w5z11n45b/IPSUR.pdf?dl=0)



This supersedes the need for other texts for this course.

The necessary pacakges to follow chapeter 4 are   "prob" and "combinat": 


install.packages("prob")   (It doesn't work with knitr)
install.packages("combinat") 



### Sample Space

The sample space of an experiment (for instance coin toss with H being heads and T being toes):  $E$ is $$S={H,T}$$

An useful function is tosscoin which generates such sample spaces: 

```{r}
library(prob)

S_space <- tosscoin(3)

```

### Probabilty distribution  

$E(x)$ the Expected Value is the mean of a probability distribution. The notation is: 

$$E(x)$$  or $$E[X]$$


### Probability measures

#### mean $\mu$

```{r}
x <- c(10,0,-2,-10)
f <- c(1/6,1/6,1/6,1/2)

mu <- sum(x*f)

mu
```

#### variance $\sigma^2$

```{r}

sigma2 <- sum((x-mu)^2*f)

sigma2
```

#### accumulated probabilities $F_X$

```{r}

F <- cumsum(f)

F
```

there is also a library `distrEx` 

### Binomial distribution

$$fx(x)=\binom{n}{x}p^x(1-p)^{n-x},\qquad  x=0,1,2,...,n$$

