---
title: "Mod 3A Binomial distribution"
author: "runlevel0"
date: "23 november 2015"
output: html_document
---

### A small function to find coeficcients given a vector x and an integer n: 

```{r}
cfnt <- function(n,x) {
        # just for clarities sake I calculate the factorials first
        fx = factorial(x)
        fn = factorial(n)
        fn_x = factorial(n-x)
        
        rval = fn / (fx*fn_x)
        
        return(rval)
}

# Example, like in Mod3A Binomial Dist, Part 4

x <- c(0:4)
n <- 4

cfnt(4,x)


```

### Binomial Probability, Example 1

The equation is: 

$$\sum\limits_{x=0}^n\binom{n}{k}p^x(1-p)^{n-x}$$

The R function that does that is dbinom(), he help funcion is somewhat confusing as it states that the arguments are x, size and *prob*ability, this is equivalent to x,n and P.

For the exaple in the video: 

```{r}
n <- 25
P <- .20
x <- 6

dbinom(x,n,P)

```
### Cumulative Binomial distribution

In the 2nd example there is a weird "bug", so that I need to be careful with that.

The function used is `pbinom`, without any extra argument it calculate the cumulative binomial distribution for $P(X>x)$, for cumulative probabilities of $P(X\leq x)$ the argument to be used is `lower.tail=FALSE`. 

_CAUTION_: In the example homework $P(X\geq5)$ (with n:10 and p:0.4) is 0.36689674, while this result is obtained in R with the following: 

```{r}
p <- .4
n <- 10
X <- 4

pbinom(X,n,p)
```
The reason is that statcrunch uses the $\geq$ operator while pbinom() uses $>$ (thus bigger than 4, or at least 5)




        
