---
title: "LSLR example with the SENIC dataset"
author: "runlevel0"
date: "October 26, 2015"
output: html_document
---

### Credits

Tutorial based on this tutorial: 
http://kenanfellows.org/kfp-cp-sites/cp19/cp19/lesson-1-least-squares-linear-regression-r/index.html

### Preparing the dataset

The dataset can be found here in XLS format: 
"http://www.unc.edu/~nielsen/soci709/data/data.htm/knnappenc01.xls"

I assume that the file is downloaded to $PWD

In order to import it it is necessary to install the package gdata: 


install.packages("gdata")

```{r}
library(gdata)


senic <- read.xls("knnappenc01.xls")
View(senic)

```



The column names need o be changed, for that I use this document as guide: 

https://datamining.bus.utk.edu/Documents/SENIC-Description.pdf

I create a vector with the ne names and aply these to the senic data frame using the paste() function: 

```{r}

vnames <- c("ID","Stay","Age","Risk","Culture","X.ray","Beds","Aff","Region","Census","Nurses","Facilities")

names(senic) <- paste(vnames)
View(senic)

```

### Plotting some data

First I prepare some variables for convenience: 

```{r}
stay <- senic$Stay
risk <- senic$Risk
```

I will first ceate a linear model and finally plot it all: 

```{r}
model1 <- lm(risk~stay)

yfit <- model1$fitted.values

plot(stay,risk, xlab="Lenght of Stay", ylab="Risk of Infection", main="Risk of Nosocomial Infection")
lines(stay,yfit)

resid <- risk-yfit #residuals
plot(stay-yfit) #residuals plot
cor(stay,risk) # correlation
```











